--- 
title: "DRAGENising COLO829 Dilution Series"
author: "Peter Diakumis"
date: "`r format(Sys.time(), '%a %Y-%b-%d')`"
site: bookdown::bookdown_site
description: "COLO829 DRAGEN"
---

```{r knitr_opts, include=F}
knitr::opts_chunk$set(echo = T)
```

```{r load_pkgs, message=F, warning=F}
require(tidyverse)
```


# Introduction
Here we're analysing the COLO829 dilution series using the Dynamic Read Analysis
for GENomics (DRAGEN) platform on the AWS Cloud.

## Data
A dilution series of varying purities (20, 40, 60, 80 and 100 per cent)
was generated from the COLO829 cell line.
The samples were sequenced with our in-house NovaSeq Illumina sequencing platform.
Paired-end FASTQ files were generated and have been uploaded to the
`umccr-primary-data-prod/Temp/2019-07-18T0233_COLO829_WGS_COLO829/` AWS S3 bucket.



| Sample  | FileName                       | Read |
|---------|--------------------------------|------|
| C020    |                                | 1    |
| C020    |                                | 2    |
| C040    |                                | 1    |
| C040    |                                | 2    |
| C060    |                                | 1    |
| C060    |                                | 2    |
| C080    |                                | 1    |
| C080    |                                | 2    |
| C100    |                                | 1    |
| C100    |                                | 2    |


